Bayesian exponential random graph modelling of KWL Burial network

### 2020-04-04 analysis/paper/paper.Rmd
work on method section and add references

Using the R language, we use Bayesian SNA to study burials from Kiwulan, an Iron Age site in northeast Taiwan. We view individual burials as actors or nodes in the social network with ties drawn between burials when the presence of the same variables that can represent the same "community" or social group. We test hypotheses about the distribution of influence in the network to identify network or corporate mode conditions. We ask the questions: 1. Do the observed burial data indicate a more clustered network than a distribution of random networks with similar qualities? 2. Whether European colonial activities in 17 century Taiwan resulted in the emergence of social inequality in an indigenous society can be detected by burials networks. We expect the network to present a higher degree of clustering (e.g. the number of completed triangles in the network) in the European contact period that might hint at social heterogeneity during this period. This study helps to expand the use of burials in understanding the indirect effects of a colonial presence on indigenous groups. A Bayesian approach enables the efficient quantification for uncertainty, parametrization, and model evaluation of social network metrics.

@@

We assume burial network represents the relations among people and social structure based on the argument that 
# Methods

Our purpose is to understand the characteristics of burial network and the mechanism of the relationship influence on the pattern of accumulation of wealth during different foreign contact periods. Previous studies have shown that there are some evidence of social inequality observed on this site but the degree and causes remains unclear. To answer our question about the shifts in social inequality during and after the arrival of foreign presence, we hypothesize:

@@

## Exponential Random Graph Models

We want to know

@@

## Statistics
ERGM- consider transitivity by taking into account high-order k-triangles. Triangles and higher order cycles

>>>>

Using the R language, we use Bayesian SNA to study burials from Kiwulan, an Iron Age site in northeast Taiwan. We view individual burials as actors or nodes in the social network with ties drawn between burials when the presence of the same variables that can represent the same "community" or social group. We test hypotheses about the distribution of influence in the network to identify network or corporate mode conditions. We ask the questions: 1. Do the observed burial data indicate a more clustered network than a distribution of random networks with similar qualities? 2. Whether European colonial activities in 17 century Taiwan resulted in the emergence of social inequality in an indigenous society can be detected by burials networks. 3. How the relations among burials may affect the quantity of burial goods? We expect the network to present a higher degree of clustering (e.g. the number of completed triangles in the network) in the European contact period that might hint at social heterogeneity during this period. This study helps to expand the use of burials in understanding the indirect effects of a colonial presence on indigenous groups. A Bayesian approach enables the efficient quantification for uncertainty, parametrization, and model evaluation of social network metrics.

@@

We assume burial network represents the relations among people and social structure based on the argument that 
## Bayesian inference for Exponential Random Graph Models

Bayesian approach to ERGMs is an efficient computational tool for social network analysis because it incorporates prior information about the network effects into the model and offers uncertainty quantification by evaluating the posterior distribution of the parameters associated with the network effects [@Caimo2015; @Nemmers2019]. This provides better estimations for complex social network models with heterogeneous data [@Caimo2017].

# Methods

Our purpose is to understand the characteristics of burial network and the mechanism of the relationship influence on the pattern of accumulation of wealth during different foreign contact periods. Previous studies have shown that there are some evidence of social inequality observed from Kiwulan but the degree over time and causes remain unclear. To answer our question for the shifts in social inequality during and after the arrival of the foreign presences, we hypothesize:

@@

The computational processes in this paper were performed by the ergm package for simulation and model specification and then bergm package using R programming [@Hunter2008; @Morris2008; @Caimo2014]. We set the number of chains to eight. For each chain, the number of burn-in iterations is 200 and the number of iterations after the burn-in is 2000. We set the number of iterations used to simulate a network y′ at each iteration to 10000.

## Statistics

@@

ERGM- consider transitivity by taking into account high-order k-triangles. Triangles and higher order cycles
